Generating Images From Captions\\ With Attention

### 2015-10-30 iclr-paper-new.tex
less ugly version of paper

@@

First, we wanted to see whether the model understood one of the most basic properties of any object, the color. In Figure~\ref{fig:genimages1}, we generated images of school buses with four different colors: yellow, red, green and blue. Although, there are images of buses with different colors in the training set, all mentioned school buses are specifically colored yellow. Despite that, the model managed to generate images of an object that is visually reminiscent of a school bus that is painted with the specified color.

\begin{figure}[!h]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\end{center}
\caption{Examples of changing the color while keeping the caption fixed.}
\label{fig:genimages1}
\vspace{-0.3cm}
\end{figure}

@@

After flipping sets of words in the captions, we were curious to see which words the model attended to when generating images. It turned out that during the generation step, the model mostly focused on the specific words (or nearby words) that carried the main semantic meaning expressed in the sentences. The attention values of words in sentences helped us interpret the reasons why the model made the changes it did when we flipped certain words. For example, in Figure~\ref{fig:attentimages1} we can see that when we flipped the word ``desert'' to ``forest'', the attention over words in the sentence did not change drastically. This suggests that, in their respective sentences, the model looked at ``desert'' and ``forest'' with relatively equal probability, and thus made the correct changes. In contrast, when we swap words ``beach'' and ``sun'', we can see a drastic change between sentences in the probability distribution over words. By noting that the model completely ignores the word ``sun'' in the second sentence, we can therefore gain a more thorough understanding of why we see no visual differences between the images generated by each caption.

\begin{figure}[!h]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[\hlcthree{A} rider \hlcone{on} a blue \hlcone{motorcycle} in the \underline{\hlctwo{desert}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-sharp.png}}\quad
%
\subfloat[\hlcthree{A} rider \hlcone{on} a blue \hlcone{motorcycle} in the \underline{\hlctwo{forest}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-sharp.png}}\quad
%
\subfloat[\hlctwo{A} \hlcone{surfer}, a woman, and a child walk on the \underline{\hlctwo{beach}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-sharp.png}}\quad
%
\subfloat[\hlcthree{A} \hlcone{surfer}, a woman, and a child walk on the \underline{\hlczero{sun}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-sharp.png}}\quad
%
\end{center}
\caption{Examples of most attended words while changing the background in the caption.}
\label{fig:attentimages1}
\vspace{-0.3cm}
\end{figure}

>>>>

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[A \underline{yellow} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{red} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{green} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
%
\subfloat[A \underline{blue} school bus parked in a parking lot.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\quad
\\
%
\subfloat[\underline{The decadent chocolate} \underline{desert} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-sharp.png}}\quad
%
\subfloat[\underline{A bowl of bananas} is on the table.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{cat}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-cat-sharp.png}}\quad
%
\subfloat[A vintage photo of a \underline{dog}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-dog-sharp.png}}\quad
%
\end{center}
\caption{\textbf{Bottom}: Examples of changing the object while keeping the caption fixed. \textbf{Top}: Examples of changing the color while keeping the caption fixed.}
\label{fig:genimages3}
\vspace{-0.3cm}
\end{figure}

@@

First, we wanted to see whether the model understood one of the most basic properties of any object, the color. In Figure~\ref{fig:genimages3}, we generated images of school buses with four different colors: yellow, red, green and blue. Although, there are images of buses with different colors in the training set, all mentioned school buses are specifically colored yellow. Despite that, the model managed to generate images of an object that is visually reminiscent of a school bus that is painted with the specified color.

@@

After flipping sets of words in the captions, we were curious to see which words the model attended to when generating images. It turned out that during the generation step, the model mostly focused on the specific words (or nearby words) that carried the main semantic meaning expressed in the sentences. The attention values of words in sentences helped us interpret the reasons why the model made the changes it did when we flipped certain words. For example, in Figure~\ref{fig:diffmodels} we can see that when we flipped the word ``desert'' to ``forest'', the attention over words in the sentence did not change drastically. This suggests that, in their respective sentences, the model looked at ``desert'' and ``forest'' with relatively equal probability, and thus made the correct changes. In contrast, when we swap words ``beach'' and ``sun'', we can see a drastic change between sentences in the probability distribution over words. By noting that the model completely ignores the word ``sun'' in the second sentence, we can therefore gain a more thorough understanding of why we see no visual differences between the images generated by each caption.

\begin{figure}[!t]
\captionsetup[subfigure]{labelformat=empty}
\vspace{-0.3cm}
\begin{center}
\subfloat[\hlcthree{A} rider \hlcone{on} a blue \hlcone{motorcycle} in the \underline{\hlctwo{desert}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-sharp.png}}\quad
%
\subfloat[\hlcthree{A} rider \hlcone{on} a blue \hlcone{motorcycle} in the \underline{\hlctwo{forest}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-sharp.png}}\quad
%
\subfloat[\hlctwo{A} \hlcone{surfer}, a woman, and a child walk on the \underline{\hlctwo{beach}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-sharp.png}}\quad
%
\subfloat[\hlcthree{A} \hlcone{surfer}, a woman, and a child walk on the \underline{\hlczero{sun}}.
]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-sharp.png}}\quad
\\
%
\subfloat[alignDRAW]{\includegraphics[width=0.23\textwidth]{figures/new/a-group-of-people-walk-on-a-beach-with-surf-boards-sharp-small.png}}\quad
%
\subfloat[LAPGAN]{\includegraphics[width=0.23\textwidth]{figures/a-group-of-people-walk-on-a-beach-with-surf-boards-lapgan-small.png}}\quad
%
\subfloat[Conv-Deconv VAE]{\includegraphics[width=0.23\textwidth]{figures/a-group-of-people-walk-on-a-beach-with-surf-boards-convdeconvvae-small.png}}\quad
%
\subfloat[Fully-Conn VAE]{\includegraphics[width=0.23\textwidth]{figures/a-group-of-people-walk-on-a-beach-with-surf-boards-fcvae-small.png}}\quad
%
\end{center}
\caption{\textbf{Bottom}: Four different models displaying results from sampling caption \textit{A group of people walk on a beach with surf boards.} \textbf{Top}: Examples of most attended words while changing the background in the caption.}
\label{fig:diffmodels}
\vspace{-0.3cm}
\end{figure}
